Adversarial Training of Invariant Features for Speech Recognition

### 2017-03-21 interspeech/paper.tex
Rearrange figure and add equation

\section{Background}
\label{sec:background}
\begin{figure*}
    \centering

    \captionsetup[subfigure]{oneside,margin={0.3cm,0cm}}
    \begin{subfigure}[b]{0.49\linewidth}
    \centering
        \includegraphics[width=0.4\linewidth]{model.pdf}
        \caption{The model consists of three neural networks. The encoder $E$ produces
        the intermediate representation $h$ which used in the recognizer $R$ and 
        in the domain discriminator $D$. The hidden representation $h$ is trained to improve
        the recognition and minimize the domain discriminator accuracy. The domain discriminator
        is a classifier trained to maximize its accuracy on the noise type
        classification task.}
        \label{fig:model}
    \end{subfigure}
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=0.7\linewidth]{wer_avg.pdf}
        \includegraphics[width=0.7\linewidth]{wer_seen_unseen.pdf}
        \caption{Top: Average performance of the baseline multi-condition and invariance model varying with  the number of noise
            conditions used for training. Bottom: Average performance on seen versus unseen noise conditions.
            Testing was performed on all wv1 conditions (Sennheiser microphone).
            }
        \label{fig:results}
    \end{subfigure}
    \caption{The model and summarized results.}
\end{figure*}
\emph{Generative Adversarial Networks} consist of two networks: the generator and the discriminator. 
    The generator network $G$ has an
    input of randomly-generated feature vectors and is asked to produce a
    sample, e.g.\ an image, similar to the images in the training set. The discriminator network $D$
    can either receive a generated image from the generator $G$ or an image
    from the training set. Its task is to distinguish
    between the ``counterfeit'' generated image and the ``genuine'' image taken from the dataset. Thus,
    the discriminator is just a classifier network with a sigmoid output layer
    and can be trained with gradient back-propagation. This gradient can be propagated further
    to the generator network (assuming that the output of the generator is
    continuous).

    The two networks in the GAN setup are competing with each other: the 
    generator is trying to deceive the discriminator network, while the discriminator tries
    to do its best to recognize if there was a deception, similar to adversarial game-theoretic settings.    
    Formally, the objective function of GAN training is
    \begin{align}
        \min_G \max_D V(D, G) = &\mathbb{E}_{\bm{x} \sim p_{\text{data}}(\bm{x})}[\log D(\bm{x})] + \\
            &\mathbb{E}_{\bm{z} \sim p_{\bm{z}}(\bm{z})}[\log (1 - D(G(\bm{z})))].
        \label{eq:gan}
    \end{align}
    The maximization over the discriminator $D$ forms a usual cross-entropy objective, the gradients are
    computed with respect to the parameters of $D$. An important property of
    this objective is that the gradient of the composition~$D(G(\cdot))$ is well
    defined. Therefore the generator~$G$ can be trained with the back-propagation
    algorithm using the gradient signal from the discriminator~$D$.
    The generator~$G$ is
    minimizing the classification objective using the gradients
    propagated through the second term. The minimization over $G$ makes it
    produce samples which $D$ classifies as originating from the train data.

@@

    Prior work by~\cite{ganin2014unsupervised} proposed a method for training a network 
    which can be adapted to new domains. The training data consists of the images
    labeled with classes of interest and separate domain (image background) labels. 
    The network has a $Y$-shaped structure: the image is fed to the
    first network which produces a hidden representation $h$. Then this 
    representation $h$ is input to two separate networks: a domain classifier network ($D$) and 
    a target classifier network ($R$). The goal of training is to learn a hidden 
    representation that is invariant to the domain labels and still performs well on 
    the target classification task, so that the domain information doesn't 
    interfere with the target classifier at test time. Similar to the GAN 
    objective, which forces the generation distribution be close to the data distribution,
    the \emph{gradient reverse method} makes domain specific distributions similar to each other.

@@

Figure~\ref{fig:model} depicts the model, which is same as the model for the 
gradient reverse method. It is a feed-forward neural network trained to predict 
the CD-HMM state, with a branch that predicts the domain (noise condition). This 
branch is discarded in the testing phase. In our experiments we
used the noise condition as the domain label, merging all noise types into one label
and defining `clean' as the other label. Our training loss function is Eq.~\ref{eq:grm} with 
$L_3$ set to $d\log(1 - \hat{d}) + (1-d)\log(\hat{d})$ for stability during training. 
$L_3$ term maximizes the probability
of an incorrect domain classification in contrast to the gradient reverse where the 
correct classification is minimized.
The terms $L_1$ and $L_2$ are 
regular cross-entropies which are minimized with corresponding parameters $\theta_E$ and $\theta_D$.
For simplicity, we use only a single hyper-parameter -- the weight of the third term.

>>>>

\section{Background}
\label{sec:background}
\emph{Generative Adversarial Networks} consist of two networks: the generator and the discriminator. 
    The generator network $G$ has an
    input of randomly-generated feature vectors and is asked to produce a
    sample, e.g.\ an image, similar to the images in the training set. The discriminator network $D$
    can either receive a generated image from the generator $G$ or an image
    from the training set. Its task is to distinguish
    between the ``counterfeit'' generated image and the ``genuine'' image taken from the dataset. Thus,
    the discriminator is just a classifier network with a sigmoid output layer
    and can be trained with gradient back-propagation. This gradient can be propagated further
    to the generator network (assuming that the output of the generator is
    continuous).

    The two networks in the GAN setup are competing with each other: the 
    generator is trying to deceive the discriminator network, while the discriminator tries
    to do its best to recognize if there was a deception, similar to adversarial game-theoretic settings.    
    Formally, the objective function of GAN training is
    \begin{align}
    \begin{split}
        \min_G \max_D V(D, G) = &\mathbb{E}_{\bm{x} \sim p_{\text{data}}(\bm{x})}[\log D(\bm{x})] + \\
            &\mathbb{E}_{\bm{z} \sim p_{\bm{z}}(\bm{z})}[\log (1 - D(G(\bm{z})))].
    \end{split}
    \label{eq:gan}
    \end{align}
    The maximization over the discriminator $D$ forms a usual cross-entropy objective, the gradients are
    computed with respect to the parameters of $D$. An important property of
    this objective is that the gradient of the composition~$D(G(\cdot))$ is well
    defined. Therefore the generator~$G$ can be trained with the back-propagation
    algorithm using the gradient signal from the discriminator~$D$.
    The generator~$G$ is
    minimizing the classification objective using the gradients
    propagated through the second term. The minimization over $G$ makes it
    produce samples which $D$ classifies as originating from the train data.

@@

    Prior work by~\cite{ganin2014unsupervised} proposed a method for training a network 
    which can be adapted to new domains. The training data consists of the images
    labeled with classes of interest and separate domain (image background) labels. 
    The network has a $Y$-shaped structure: the image is fed to the
    first network which produces a hidden representation $h$. Then this 
    representation $h$ is input to two separate networks: a domain classifier network ($D$) and 
    a target classifier network ($R$). The goal of training is to learn a hidden 
    representation that is invariant to the domain labels and still performs well on 
    the target classification task, so that the domain information doesn't 
    interfere with the target classifier at test time. Similar to the GAN 
    objective, which forces the generation distribution be close to the data distribution,
    the \emph{gradient reverse method} makes domain specific distributions similar to each other.
\begin{figure}[t]
    \centering

    \centering
        \includegraphics[width=0.4\linewidth]{model.pdf}
        \caption{The model consists of three neural networks. The encoder $E$ produces
        the intermediate representation $h$ which used in the recognizer $R$ and 
        in the domain discriminator $D$. The hidden representation $h$ is trained to improve
        the recognition and minimize the domain discriminator accuracy. The domain discriminator
        is a classifier trained to maximize its accuracy on the noise type
        classification task.}
        \label{fig:model}
\end{figure}
\begin{figure}[t]
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=1.1\linewidth]{wer_avg.pdf}
        \caption{Average performance of the baseline multi-condition and invariance model varying with  the number of noise
            conditions used for training.}
        \label{fig:results}
    \end{subfigure}
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=1.1\linewidth]{wer_seen_unseen.pdf}
        \caption{Average performance on seen versus unseen noise conditions.
            Testing was performed on all wv1 conditions (Sennheiser microphone).
            }
    \end{subfigure}
    \caption{Summarized results.}
    \label{fig:results}
\end{figure}

@@

Figure~\ref{fig:model} depicts the model, which is same as the model for the 
gradient reverse method. It is a feed-forward neural network trained to predict 
the CD-HMM state, with a branch that predicts the domain (noise condition). This 
branch is discarded in the testing phase. In our experiments we
used the noise condition as the domain label, merging all noise types into one label
and defining `clean' as the other label. Our training loss function is  
\begin{align}
    \begin{split}
    L = L_1(\hat{y}, y; \theta_R, \theta_E) + 
    \alpha L_2(\hat{d}, d; \theta_D) -\\
    \beta [d\log(1 - \hat{d}) + (1-d)\log(\hat{d})],
    \end{split}
    \label{eq:our}
\end{align}
where $d$ is the domain label and $\hat{d}$ is the predicted domain.
The~$L_3$ term from Eq.~\ref{eq:grm} is defined according to the standard GAN
objective for stability during training. 
This term maximizes the probability
of an incorrect domain classification in contrast to the gradient reverse where the 
correct classification is minimized.
The terms $L_1$ and $L_2$ are 
regular cross-entropies which are minimized with corresponding parameters $\theta_E$ and $\theta_D$.
For simplicity, we use only a single hyper-parameter -- the weight of the third term.
